Many Analystis Project

### 2022-03-12 History/analysis-v-use.Rmd
order files
create history foldrer

df <- d %>%
  dplyr::mutate(male2 = ifelse(gender != "man", 1 , 2)) %>% # for index categorical variable, not change of meaning for gender. male and people who do not identify as male.
  dplyr::mutate(male = factor(ifelse(gender != "man", "male" , "notmale"))) %>%
  rename(
    rel_CHURCHFREQ   = rel_1,
    # factor need to recode (eg 7 as 0)// yikes factor transformed into a number
    rel_PRAYERFREQ = rel_2,
    # factor need to recode (eg. 7 as 0)// yikes factor transformed into a number
    IS_RELIIGOUS = rel_3,
    # factor 1 = yes, 2 = no, 3 = atheist// yikes factor transformed into a number
    # NOOO revers scorred (1= religious, 2= not religious, 3=atheist) [R] So note that 3 = religious!!
    BELONGS_DENOMINATION = rel_4,
    # relig
    rel_EXTENTBELIEVEGOD = rel_5,
    # do you belong to a religion or religious denomination? 1 = yes, 2 = no (!)
    rel_EXTENTBELIEVEAFTERLIFE = rel_6,
    rel_EXTENTSPIRITUAL  = rel_7,
    rel_IMPORTANCERELIGIOUSLIFE = rel_8,
    # 1 to five
    rel_IMPORTANCEBELIEVEGOD = rel_9,
    # 1 to five
    wb_genLIFEQUALITY = wb_gen_1,
    # not defined # also remove second underscore, which BRMS doesn't like
    wb_genSATHEALTH = wb_gen_2,
    # not defined
    wb_phyPAIN = wb_phys_1,
    wb_physNEEDSMEDICALTREAT =  wb_phys_2,
    wb_physHASENERGY =  wb_phys_3,
    wb_physMOBILITY = wb_phys_4,
    wb_physSLEEP = wb_phys_5,
    wb_physCANDODAILYACTIVITIES  = wb_phys_6,
    wb_physSATCAPACITYWORK  = wb_phys_7,
    wb_psychENJOYLIFE = wb_psych_1,
    wb_psychMEANING  = wb_psych_2,
    wb_psychCONCENTRATE  = wb_psych_3,
    wb_psychLIKESAPPEARANCE  = wb_psych_4,
    wb_psychSATSELF  = wb_psych_5,
    wb_psychANXIETY  = wb_psych_6,
    wb_socSATPERSONALRELATIONSHIPS  = wb_soc_1,
    wb_socSATSUPPORTFRIENDS  = wb_soc_2
    #   wb_socSATSEX   = wb_soc_3,
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = as.factor(IS_RELIIGOUS),
    denomination = as.factor(denomination),
    ethnicity = as.factor(ethnicity),
    country = as.factor(country)
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = recode_factor(
      IS_RELIIGOUS,
      "0" = "atheist",
      "0.5" = "not_religious",
      "1" = "religious"
    )
  )
max(df$rel_EXTENTBELIEVEGOD)
max(df$rel_CHURCHFREQ)
length(unique(df$country))
table(df$country)
```

@@

d1 <- df %>%
  dplyr::filter(
   #  !is.na(wb_psychANXIETY),
   #  !is.na(age),
   #  !is.na(rel_CHURCHFREQ),
   # # !is.na(wb_psychMEANING),
   #  !is.na(male),
   #  !is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    religious = as.integer(IS_RELIIGOUS), #(1= religious, 2= not religious, 3=atheist) [R]
    #put outcome in ST units (see McElreath 2021)  # not necessary
    #age_s = scale(age),
    ch = rel_CHURCHFREQ,
  #  mn  = wb_psychMEANING,
    edu = education,
    bg =  rel_EXTENTBELIEVEGOD#,
  #  ch_s = scale(rel_CHURCHFREQ),
  #  mn_s = scale(wb_psychMEANING),
   # bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx,
                ch,
                age,
                ses,
                #    mn,
                edu,
                bg,
                # anx_s,
                # age_s,
                #  ch_s,
                #  mn_s,
                edu,
                country,
                male,
                religious,
                #   bg_s,
                denomination,
                wb_psychANXIETY)

@@

table

```{r}
lt <-table1::table1(~  denomination, data = d1, transpose=F)
lt
lt <-table1::table1(~ ch + religious + age + male + edu + ses + denomination |country, data = d1, transpose=F)
lt
kable(as.data.frame(lt), booktabs=TRUE, "latex")

nrow(dr)
```

@@

miss_graph<- gg_miss_upset(dff)
miss_graphR <-image_ggplot(miss_graph)
# save graph
miss_graph

ggsave(miss_graph,
  path = here::here("figs"),
  width = 16,
  height = 9,
  units = "in",
  filename = "miss_graph.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

table1::table1(~ ch |religious, data = d1)

@@

```{r}
library(mice)
library(tidyverse)
d2<-mice(d1)

#d3<-complete(d2)
#saveRDS(d3,here::here("mods","d3"))
#d3 <-readRDS(here::here("mods","d3"))
d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country,religious)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         religious = factor(religious),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))

@@

d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country,religious)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country),
         religious = as.factor(religious))

@@

# weighted for religious only

@@

# fine, well below 10
max(dr$ipwCH)
```

## Tables

```{r}
lt <-table1::table1(~ religious|ch_ord, data = dp)

kable(as.data.frame(lt), booktabs=TRUE, "latex")

nrow(dr)
```

### Simulation

```{r}
#\begin{lstlisting}[language=R]

set.seed(123)
sim_fun_A = function() {
  n <- 1000
  U <- rnorm(n, 1) # Unmeasured distress 
  A <- rnorm(n, 1) # religious service attendance,
  M <- rnorm(n , A + U)# rel id
  Y <- rnorm(n , - A*.2 + U + M*.1) #  distress reduced by attendance.

# Religious id, caused by attendance + distress

# simulate data
simdat_A <- data.frame(
  M = L, # rel id
  A = A, # rel service
  U = U, # distressing events (unmeasured)
  Y = Y ) # outcome

sim_A <- lm(Y ~ A + M, data = simdat_A)
sim_A
}

# Replicate including the mediator
r_lm_A <- NA
r_lm_A = replicate(100, sim_fun_A(), simplify = FALSE )

# average over outcomes: effect of religion is attenuated
parameters::pool_parameters(r_lm_A)

## Repeat but with no mediator in model
set.seed(123)
sim_fun_B = function() {
  n <- 1000
  U <- rnorm(n, 1) # Unmeasured distress 
  A <- rnorm(n, 1) # religious service attendance,
  M <- rnorm(n , A + U)# rel id + distress
  Y <- rnorm(n , - A *.2 + U + M*.1) #  distress reduced by attendance.

# simulate data
simdat_B <- data.frame(
  M = L, # rel id
  A = A, # rel service
  U = U, # distressing events (unmeasured)
  Y = Y ) # outcome

# Only exposure
sim_B <- lm(Y ~ A, data = simdat_A)
sim_B
}

# Replication 1000xs
r_lm_B <- NA
r_lm_B = replicate(100, sim_fun_B(), simplify = FALSE )

# average over outcomes: effect of religion is attenuated
parameters::pool_parameters(r_lm_B)

#\end{lstlisting}
```

```{r}
dr$ch_ord <- factor(dr$ch, ordered=TRUE)
table(dr$ch_ord)

levels(dr$ch_ord)<-c("never","rarely","1xpy","holydays","1xpm","1xpw",">1xpw")

levels(dr$ch_ord)
is.ordered(dr$ch_ord)

#saveRDS(dr, here::here("mods","dr"))

# saveRDS(d1p, here::here(
#   "mods","d1p"
# ))

b_orR <- brm(
  anx_s|weights(ipwCH) ~ mo(ch_ord) + (1 + mo(ch_ord) | country),
  data = dr,
   prior = c(
    prior(student_t(3, 0, .5), class = Intercept),
    prior(normal(-.05,.1), class = "b"),
    prior(dirichlet(1,1,1,1,1,1), class = "simo", coef = moch_ord1)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","b_orR")
)

summary(b_orR)

prior_summary(b_orR)

church_plot_R <-plot(ggeffects::ggemmeans(b_or, terms = "ch_ord")) +   xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
  theme_classic()
church_plot_R

### EEMEANS
 b_orR %>% 
  emmeans(~ ch_ord,
          at = list(ch_ord = c("never",">1xpw"),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise")

effect_draws_b_orR <-  b_orR %>% 
  emmeans(~ ch_ord,
         at = list(ch_ord = c("never",">1xpw"),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise") %>%
  gather_emmeans_draws()

effect_draws_b_orR %>% mean_hdi()

#SE = (upper limit – lower limit) / 3.92.

# STANDARD ERROR
Roa <- effect_draws_b_orR %>% mean_hdi() 
(Roa$.upper - Roa$.lower)/3.92 #

# SE = .0.06751772

library(EValue)
evalues.OLS(-0.208, se = 0.06751772, sd = 1, delta = 1)
#             point    lower     upper
# RR       0.8275548 0.733842 0.9332348
# E-values 1.7101772       NA 1.3484170
bias_plot(0.9332348, xmax = 6)

average_marginal_effectR <- ggplot(effect_draws_b_orR, aes(x = .value)) +
    stat_halfeye(fill = "dodgerblue") +
  labs(x = "Average marginal effect of church attenance on anxiety", y = "Density",
       subtitle = "Marginal effect (never vs. 1xpw): continuous model") +
  theme_classic() +
       scale_x_continuous(limits=c(-.6,.3)) +
  theme(legend.position = "top")

average_marginal_effectR

grand_mean_ameR <- b_orR %>% 
  emmeans(~ ch_ord,
          at = list(ch_ord = c("never",">1xpw")),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

plot_grand_mean_ameR <- ggplot(grand_mean_ameR, 
                                   aes(x = .value)) +
  stat_halfeye(fill = palette_okabe_ito(order = 5)) +
  labs(x = "Average marginal effect of church attenance on anxiety", y = "Density",
       subtitle = "Marginal effect (never vs. 1xpw): monotonic model") +
  theme_classic() +
    scale_x_continuous(limits=c(-.6,.3)) +
   theme(legend.position = "bottom",
         legend.title = element_text(size = 5),
          legend.text = element_text(size = 2)) 
plot_grand_mean_ameR

grand_mean_autonomy_distR <- b_orR %>% 
  epred_draws(newdata = expand_grid(ch_ord = c("never",
                                               #"rarely","1xpy","holydays","1xpm","1xpw",
                                               ">1xpw")), 
              re_formula = NA)

plot_grand_mean_ordR <- ggplot(grand_mean_autonomy_distR, 
                                   aes(x = .epred, 
                                       fill = ch_ord)) +
  scale_fill_okabe_ito() +
    stat_halfeye(slab_alpha = 0.7) +
    scale_x_continuous(limits=c(-.6,.4)) +
  labs(x = "Predicted anxiety (standardised)", y = "Density",
       fill = "Church frequency",
       subtitle = "Posterior predictions: monotonic model") +
  theme_classic() +
     theme(legend.position = "bottom",
         legend.title = element_text(size = 12),
          legend.text = element_text(size = 8))

graph_r<- plot_grand_mean_ameR + plot_grand_mean_ordR + plot_annotation(tag_levels = "a",  title = "Religious only model")
yola

ggsave(
  graph_r,
  path = here::here("figs"),
  width = 12,
  height = 6,
  units = "in",
  filename = "graph_r.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

## include religion

```{r}
library(splines)

ipb_ch_ln_no_mediation <- geeglm(
  anx_s ~ ch,
  data = d1p,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)

## Model misspecification 
ipb_ch_ln_mediation <- geeglm(
  anx_s ~ ch + religious,
  data = d1p,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
saveRDS(ipb_ch_ln_mediation, here::here("mods","ipb_ch_ln_mediation"))
saveRDS(ipb_ch_ln_no_mediation, here::here("mods","ipb_ch_ln_no_mediation"))

model_parameters(ipb_ch_ln_mediation)
model_parameters(ipb_ch_ln_no_mediation)

plot(ggeffects::ggemmeans(ipb_ch_ln_mediation, terms = "ch"), add.data = TRUE)

ipb_ch<- geeglm(
  anx_s ~  bs(ch),
  data = d1p,  
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
saveRDS(ipb_ch, here::here("mods","ipb_ch"))
model_parameters(ipb_ch)

plot(ggeffects::ggemmeans(ipb_ch, terms = "ch[all]"), add.data = TRUE
     )

## Rel only

library(splines)
ipb_ch_lnR<- geeglm(
  anx_s ~ ch,
  data = dr,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
#saveRDS(ipb_ch_lnR, here::here("mods","ipb_ch_lnR"))
model_parameters(ipb_ch_lnR)

plot(ggeffects::ggemmeans(ipb_ch_lnR, terms = "ch"), add.data = TRUE
     )

ipb_chR<- geeglm(
  anx_s ~  bs(ch),
  data = dr,  
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
saveRDS(ipb_chR, here::here("mods","ipb_ch"))
model_parameters(ipb_chR)

plot(ggeffects::ggemmeans(ipb_chR, terms = "ch[all]"), add.data = TRUE
     )

@@

abs(min(d1p$ch_s) - max(d1p$ch_s))
# 3.064032

@@

listout <- readRDS(here::here("mods","listout"))
modmc_wt_priorStrong <- brm(
  anx_s|weights(ipwCH) ~ bs(ch_s) + (1 + ch_s | country),
  data = d1p,
    prior = c(
    prior(student_t(3, 0,.25), class = Intercept),
    prior(normal(-.05, .1), class = b)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","modmc_wt_priorStrong")
)

## Table
parameters::parameters(
  modmc_wt_priorStrong,
  test = "pd",
  component = "all",
  priors = FALSE, 
  ci_method = "hdi",
#  effects = "fixed",
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 3)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    mutate_all(funs(str_replace(., "bs", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Parameter estimates for continuous (spline) model of religious service on anxiety") %>%
    print()

# prior summary

prior_summary(modmc_wt_priorStrong)

##### TeST PRIORS
modmc_wt_priorStrong_TEST <- brm(
  anx_s|weights(ipwCH) ~ bs(ch_s) + (1 + ch_s | country),
  data = d1p,
    prior = c(
    prior(student_t(3, 0,.25), class = Intercept),
    prior(normal(-.05, .1), class = b)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  sample_prior = "only",
  backend = "cmdstanr",
 file = here::here("mods","modmc_wt_priorStrong")
)

@@

# difference
abs(maxchur-minchur)

@@

@@

effect_draws_cn <-  modmc_wt_priorStrong %>% 
  emmeans(~ ch_s,
          at = list(ch_s = c(-0.8321022,2.23193),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

# marginal mean 
effect_draws_cn %>% mean_hdi()

# marginal mean 
effect_draws_cn %>% mean_hdi() 
effect_draws_cn

average_marginal_effect <- ggplot(effect_draws_cn, aes(x = .value)) +
    stat_halfeye(fill = "dodgerblue") +
  labs(x = "Average marginal effect of church attenance on anxiety", y = "Density",
       subtitle = "Marginal effect (never vs. 1xpw): continuous model") +
  theme_classic() +
       scale_x_continuous(limits=c(-.6,.3)) +
  theme(legend.position = "top")

@@

grand_mean <- modmc_wt_priorStrong %>% 
  epred_draws(newdata = expand_grid(ch_s = seq(-0.8321022, 2.23193, by = 0.05)), 
              re_formula = NA)

  plot_grand_mean <- ggplot(grand_mean, 
                                 aes(x = ch_s, y = .epred)) +
  stat_lineribbon() +
  scale_fill_brewer(palette = "Blues") +
 # scale_fill_viridis_d(palette = "Blues") +
  labs(x = "Frequency of religious service attendance (SD)", 
       y = "Predicted anxiety (SD)",
       fill = "95 HPD interval",
       subtitle = "Posterior predictions: continuous model") +
     theme_classic() +
  theme(legend.position = "bottom",
        legend.title = element_text(size = 10),
          legend.text = element_text(size = 8))

plot_grand_mean
plot_result <- average_marginal_effect + plot_grand_mean +  plot_annotation(tag_levels = "a")
plot_result

ggsave(
  plot_result,
  path = here::here("figs"),
  width = 16,
  height = 9,
  units = "in",
  filename = "plot_result.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

# sensitivity = Church
#yola

#SE = (upper limit – lower limit) / 3.92.

ta <- effect_draws_cn %>% mean_hdi() 
ta
(ta$.upper - ta$.lower)/3.92 #

evalues.OLS(-0.147 , se = 0.05607611, sd = 1, delta = 1.1)
# 
#              point     lower     upper
# RR       0.8631671 0.7734115 0.9633389
# E-values 1.5870732        NA 1.2368137

# multibias
multi_evalue(est = RR( 0.8631671), biases = selection())

#
bias_plot(0.8631671, xmax=5)

multi_bound(multi_bias(confounding()),
                RRAUc = 2.2, RRUcY = 1.7)
```

## Scaled 0-1

```{r, cache = TRUE}
d1p<-readRDS(here::here("mods","d1p"))

dchr_sc <- ipw::ipwpoint(
  exposure = ch,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~ age_s + edu_s + male_2 + ses_s + country,
  trunc = 0.01,
  data = as.data.frame(d1p)
)

dp <- d1p %>% 
  mutate(ipwCH = dchr_sc$weights.trunc)

# fine, well below 10
max(dp$ipwCH)

@@

# Montonic effects

```{r}
# bayesian monotonic effects

dp$ch_ord <- factor(dp$ch, ordered=TRUE)
table(dp$ch_ord)

levels(dp$ch_ord)<-c("never","rarely","1xpy","holydays","1xpm","1xpw",">1xpw")

levels(dp$ch_ord)
is.ordered(dp$ch_ord)

#saveRDS(dp, here::here("mods","dp"))
dp<-readRDS(here::here("mods","dp"))
```

## ORDINAL MODEL

```{r}
## Bayesian wieghted regression 
b_or <- brm(
  anx_s|weights(ipwCH) ~ mo(ch_ord) + (1 + mo(ch_ord) | country),
  data = dp,
   prior = c(
    prior(student_t(3, 0, .5), class = Intercept),
    prior(normal(-.05,.1), class = "b"),
    prior(dirichlet(1,1,1,1,1,1), class = "simo", coef = moch_ord1)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","b_or")
)

summary(b_or)

prior_summary(b_or)
summary(b_or)

church_plot <-plot(ggeffects::ggemmeans(b_or, terms = "ch_ord")) +   xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
  theme_classic()
church_plot
```

## Tables

```{r}
# tab_or <- model_parameters(b_or,   verbose = F, ci_method = "hdi",test = c("pd"))
# kbl(tab_or, "latex",booktabs=T)

# sjstats::tidy_stan(tab_or)

# library(broom.mixed)
# tidy(
#   b_or,
#  # parameters = NA,
#   effects = c("fixed", "ran_pars"),
#   robust = FALSE,
#   conf.int = TRUE,
#   conf.level = 0.95,
#   conf.method = c("HPDinterval"),
#   fix.intercept = TRUE
# )

parameters::parameters(
  b_or,
  test = "pd",
  component = "all",
  priors = FALSE, 
  ci_method = "hdi",
#  effects = "fixed",
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 3)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    mutate_all(funs(str_replace(., "_moch", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Parameter estimates for model of religious service on anxiety") %>%
    print()
```

```{r}
# pord<-brms::conditional_effects(b_or, "ch_ord", 
#                               spaghetti = T,
#                               ndraws = 1000,
#                               categorical = F,
#                               prob = .9,
#                               method = 'fitted')
# 
# 
# church_plot <- plot(pord, plot = FALSE)[[1]]   +  xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
# subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
#   theme_classic()
# church_plot
library(tidybayes)

summary(b_or)
### EEMEANS
 b_or %>% 
  emmeans(~ ch_ord,
          at = list(ch_ord = c("never",">1xpw"),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise")

  effect_draws <-  b_or %>% 
  emmeans(~ ch_ord,
         at = list(ch_ord = c("never",">1xpw"),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise") %>%
  gather_emmeans_draws()

# linear model, for EVALUES
effect_draws_or <-  b_or %>% 
  emmeans(~ ch_ord,
         at = list(ch_ord = c("never",">1xpw"),
                    country = NA),
          epred = TRUE) %>%
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()
effect_draws_or
# marginal mean 
effect_draws_or %>% mean_hdi()

# calculate standard error
# 
# se <- function(x) sqrt(var(x) / length(x))
# 
# summary(b_or)
# se(effect_draws_ln$.value)
library(tidybayes)
library(ggokabeito)   # Neat accessible color palette
# emmeans()-based difference across autonomy
grand_mean_ame <- b_or %>% 
  emmeans(~ ch_ord,
          at = list(ch_ord = c("never",">1xpw")),
          epred = TRUE, re_formula = NA) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

>>>>

df <- d %>%
  dplyr::mutate(male2 = ifelse(gender != "man", 1 , 2)) %>% # for index categorical variable, not change of meaning for gender. male and people who do not identify as male.
  dplyr::mutate(male = factor(ifelse(gender != "man", "male" , "notmale"))) %>%
  rename(
    rel_CHURCHFREQ   = rel_1,
    # factor need to recode (eg 7 as 0)// yikes factor transformed into a number
    rel_PRAYERFREQ = rel_2,
    # factor need to recode (eg. 7 as 0)// yikes factor transformed into a number
    IS_RELIIGOUS = rel_3,
    # factor 1 = yes, 2 = no, 3 = atheist// yikes factor transformed into a number
    # NOOO revers scorred (1= religious, 2= not religious, 3=atheist) [R] So note that 3 = religious!!
    BELONGS_DENOMINATION = rel_4,
    # relig
    rel_EXTENTBELIEVEGOD = rel_5,
    # do you belong to a religion or religious denomination? 1 = yes, 2 = no (!)
    rel_EXTENTBELIEVEAFTERLIFE = rel_6,
    rel_EXTENTSPIRITUAL  = rel_7,
    rel_IMPORTANCERELIGIOUSLIFE = rel_8,
    # 1 to five
    rel_IMPORTANCEBELIEVEGOD = rel_9,
    # 1 to five
    wb_genLIFEQUALITY = wb_gen_1,
    # not defined # also remove second underscore, which BRMS doesn't like
    wb_genSATHEALTH = wb_gen_2,
    # not defined
    wb_phyPAIN = wb_phys_1,
    wb_physNEEDSMEDICALTREAT =  wb_phys_2,
    wb_physHASENERGY =  wb_phys_3,
    wb_physMOBILITY = wb_phys_4,
    wb_physSLEEP = wb_phys_5,
    wb_physCANDODAILYACTIVITIES  = wb_phys_6,
    wb_physSATCAPACITYWORK  = wb_phys_7,
    wb_psychENJOYLIFE = wb_psych_1,
    wb_psychMEANING  = wb_psych_2,
    wb_psychCONCENTRATE  = wb_psych_3,
    wb_psychLIKESAPPEARANCE  = wb_psych_4,
    wb_psychSATSELF  = wb_psych_5,
    wb_psychANXIETY  = wb_psych_6,
    wb_socSATPERSONALRELATIONSHIPS  = wb_soc_1,
    wb_socSATSUPPORTFRIENDS  = wb_soc_2
    #   wb_socSATSEX   = wb_soc_3,
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = as.factor(IS_RELIIGOUS),
    denomination = as.factor(denomination),
    ethnicity = as.factor(ethnicity),
    country = as.factor(country)
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = recode_factor(
      IS_RELIIGOUS,
      "0" = "atheist",
      "0.5" = "not_religious",
      "1" = "religious"
    )
  )
max(df$rel_EXTENTBELIEVEGOD)
max(df$rel_CHURCHFREQ)
```

@@

d1 <- df %>%
  dplyr::filter(
   #  !is.na(wb_psychANXIETY),
   #  !is.na(age),
   #  !is.na(rel_CHURCHFREQ),
   # # !is.na(wb_psychMEANING),
   #  !is.na(male),
   #  !is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    religious = as.integer(IS_RELIIGOUS), #(1= religious, 2= not religious, 3=atheist) [R]
    #put outcome in ST units (see McElreath 2021)  # not necessary
    #age_s = scale(age),
    ch = rel_CHURCHFREQ,
  #  mn  = wb_psychMEANING,
    edu = education,
    bg =  rel_EXTENTBELIEVEGOD#,
  #  ch_s = scale(rel_CHURCHFREQ),
  #  mn_s = scale(wb_psychMEANING),
   # bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx,
                ch,
                age,
                ses,
                #    mn,
                edu,
                bg,
                # anx_s,
                # age_s,
                #  ch_s,
                #  mn_s,
                edu,
                country,
                male,
                religious,
                #   bg_s,
                wb_psychANXIETY)

@@

@@

miss_graph<- gg_miss_upset(dff)
miss_graph <-image_ggplot(miss_graph)
# save graph
str(miss_graph)

ggsave(miss_graph,
  path = here::here("figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "miss_graph.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

@@

```{r}
library(mice)
library(tidyverse)
#d2<-mice(d1)
#d3<-complete(d2)
#saveRDS(d3,here::here("mods","d3"))
d3 <-readRDS(here::here("mods","d3"))
d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))

pred <- ggeffects::ggemmeans(modelsCH[[1]], terms = c("ch_s[all]"))
pred

plot(pred,
    # add.data=T,dot.alpha=.1, 
     facets = F)  + scale_y_continuous(limits=c(-.5,.5)) + theme_classic() + ggtitle("") # title to be suppled
parameters::pool_parameters(modelsCH)

parameters::pool_parameters(modelsCH)
#parameters::pool_parameters(modelschG)

@@

d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))

@@

# weighted

@@

# fine, well below 10
max(dr$ipwCH)

# saveRDS(d1p, here::here(
#   "mods","d1p"
# ))
```

```{r}
library(splines)
ipb_ch_ln<- geeglm(
  anx_s ~ ch_s,
  data = d1p,
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
saveRDS(ipb_bg, here::here("mods","ipb_bg_ln"))

ipb_ch<- geeglm(
  anx_s ~  bs(ch_s),
  data = d1p,  
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
saveRDS(ipb_ch, here::here("mods","ipb_ch"))

@@

model_parameters(ipb_ch)

min(d1p$ch_s) + max(d1p$ch_s)

@@

@@

@@

p0priorTEST<-brms::conditional_effects(modmc_wt_priorStrong_TEST, "ch_s", 
                              spaghetti = T,
                              ndraws = 1000,
                              categorical = F,
                              prob = .95,
                              method = 'fitted')

church_plot_test_strong <- plot(p0priorTEST, plot = FALSE)[[1]]   +  xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Prior Sanity Check: Baysian Multi-level Model", subtitle = "Sampling from STRONG Priors Only") + scale_y_continuous(limits = c(-.5,.25))+ 
  theme_classic()
church_plot_test_strong

pred_brms

p0priorTEST_weak<-brms::conditional_effects(modmc_wt_prior_weak, "ch_s", 
                              spaghetti = T,
                              ndraws = 1000,
                              categorical = F,
                              prob = .95,
                              method = 'fitted')

church_plot_test_weak <- plot(p0priorTEST_weak, plot = FALSE)[[1]]   +  xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Prior Sanity Check: Baysian Multi-level Model", subtitle = "Sampling from WEAK Priors Only") + scale_y_continuous(limits = c(-.5,.5))+ 
  theme_classic()
church_plot_test_weak

@@

effect_draws <-  modmc_wt_priorStrong %>% 
  emmeans(~ ch_s,
          at = list(ch_s = c(-0.8321022,2.23193),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

# marginal mean 
effect_draws %>% mean_hdi()

# linear model, for EVALUES
effect_draws_ln <-  modmc_wt_linear %>% 
  emmeans(~ ch_s,
          at = list(ch_s = c(-0.8321022,2.23193),
                    country = NA),
          epred = TRUE) %>% 
  contrast(method = "revpairwise") %>% 
  gather_emmeans_draws()

# marginal mean 
effect_draws_ln %>% mean_hdi()

average_marginal_effect <- ggplot(autonomy_effect_draws, aes(x = .value)) +
  stat_halfeye(fill = "dodgerblue") +
  labs(x = "Average marginal effect of church attendance", y = "Density") +
  theme_clean() +
  theme(legend.position = "top")

@@

grand_mean <- modmc_wt_priorStrong %>% 
  epred_draws(newdata = expand_grid(ch_s = seq(minchur, maxchur, by = 0.05)), 
              re_formula = NA)

  plot_grand_mean <- ggplot(grand_mean, 
                                 aes(x = ch_s, y = .epred)) +
  stat_lineribbon() +
  scale_fill_brewer(palette = "Blues") +
 # scale_fill_viridis_d(palette = "Blues") +
  labs(x = "Frequency of religious service attendance (standard deviation units)", 
       y = "Predicted anxiety (standard deviation units)",
       fill = "95 HPD interval") +
  theme_clean() +
  theme(legend.position = "top")

 plot_result <- average_marginal_effect + plot_grand_mean +  plot_annotation(tag_levels = "a")
plot_result

ggsave(
  plot_result,
  path = here::here("figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "plot_result.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

# sensitivity = Church
evalues.OLS(-0.1093  , se = 0.0172, sd = 1, delta = 1.4)

evalues.OLS(-0.2649 , se = 0.0648, sd = 1, delta = 1)

evalues.OLS(-0.17 , se = 0.05, sd = 1, delta = 1)
#1.61

# multibias
multi_evalue(est = RR(0.981), biases = selection())

#
bias_plot(rr = 0.857, xmax=5)

multi_bound(multi_bias(confounding()),
                RRAUc = 2.2, RRUcY = 1.7)

biases <- multi_bias(confounding(), selection("S = U"),
                         misclassification("exposure",
                         rare_outcome = TRUE, rare_exposure = FALSE))

@@

## Bayesian weighted regression correct sample

```{r}
## Bayesian wieghted regression

```{r}
b_ln <- brm(
  anx_s|weights(ipwCH) ~ ch_s + (1 + ch | country),
  data = dr,
    prior = c(
    prior(normal(0, .1), class = Intercept),
    prior(normal(-.1,.1), class = b)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","b_ln")
)

summary(b_ln)

prior_summary(b_ln)
summary(b_ln)
